%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
% https://www.sharelatex.com/project/54c10798187b747c47914966

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\usepackage{sans}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Akash Shende} % Your name
\address{Pune City, India} % Your address
\address{(+91)~$\cdot$~8055~$\cdot$~737517 \\ akash0x53s@gmail.com} % Your phone number and email

\begin{document}

\begin{rSection}{Summary}
3+ years working experience of software design \& development and DevOps. Experienced in writing standalone apps to distributed modules in Python \& C. Hands-on experience in cutting edge deployment tools like Docker, Ansible. 
\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of Pune, Pune, India} \hfill {\em May 2013} \\ 
Bachelor of Engineering in Computer Engineering \\
Percentage: 62.40\%

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Vaultize Technologies}{Oct 2013 - Present}{Python Developer}{Pune, India}

\item Developed the most efficient PST backup solution.
\item Developed ICAP agent to communicate with Antivirus \& DLP engines.
\item Developed Eventhub, which is message passing system designed for Vaultize.
\item Developed Resumable file upload protocol - allowed user to upload large files with pause-resume ability.
\item Volunteered to assess \& fix vulnerabilities.
\item Worked with DevOps team to build Docker images, and configured application server (uWsgi).
\item Worked with DevOps team to optimize System configurations.
\item Built Jenkins pipeline to generate daily builds and execute automated test cases.
\item Built infrastructure with Docker, Vagrant \& Ansible for QA automation.
\end{rSubsection}

\begin{rSubsection}{Individual FOSS Contribution}{2014-Present}{On github.com/akash0x53}{}
\item Contribution to Linux Kernel (signed as akash0x53s@gmail.com).
\item Sent PR to add support for SameSiteCookie in core CPython \& web.py framework.
\item Contribution to more than 10 open source projects.
\end{rSubsection}

%------------------------------------------------


\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages & Python, C, Go;\\
Web Technologies \& Frameworks & HTML5, jQuery, AngularJS, WebPy; \\
DevOps & Docker, Vagrant, Ansible; \\
Protocols \& APIs & HTTP, ICAP; \\
Databases & MongoDB; \\
Certificate & MongoDB for Developers (MongoDB University).
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}

